\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-06-18 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
updating proof in the appendix

To set up a variational recursion of the form \eqref{InfiniteDimProxOpDef} for \eqref{TransformedPDEivp}, we set $(\Phi,{\rm{dist}}) \equiv \left(\widetilde{\Phi},\widetilde{W}\right)$ where
\begin{align}
\widetilde{\Phi}(\tilde{\rho}) := \int_{\mathbb{T}^{n} \times \mathbb{R}^{n}}\left(F(\boldsymbol{\eta})+\frac{1}{2} \log \tilde{\rho}\right) \tilde{\rho}\: \mathrm{d} \boldsymbol{\xi} \mathrm{d} \boldsymbol{\eta},
\label{Phitilde}	
\end{align}
and 
\begin{align}
\widetilde{W}^{2}\left(\tilde{\varrho}, \tilde{\varrho}_{k-1}\right):=&\inf _{\pi \in \Pi\left(\tilde{\varrho}, \tilde{\varrho}_{k-1}\right)}\!\int_{\mathbb{T}^{2 n} \times \mathbb{R}^{2 n}}\!\!\left\{\left\|\overline{\boldsymbol{\eta}}-\boldsymbol{\eta}+h \nabla_{\boldsymbol{\xi}} U(\boldsymbol{\xi})\right\|_{2}^{2}\right.\nonumber\\
&\hspace*{-0.2in}\left.+12\left\|\frac{\overline{\boldsymbol{\xi}}-\boldsymbol{\xi}}{h}-\frac{\overline{\boldsymbol{\eta}}+\boldsymbol{\eta}}{2}\right\|_{2}^{2}\right\} \mathrm{d} \pi(\boldsymbol{\xi}, \boldsymbol{\eta}, \overline{\boldsymbol{\xi}}, \overline{\boldsymbol{\eta}}).
\label{Wtilde}	
\end{align}
In \eqref{Wtilde},

That the sequence of functions $\{\tilde{\varrho}_{k}\}$ for $k\in\mathbb{N}$, generated by the proximal recursion
\begin{align}
\tilde{\varrho}_{k} = {\text{prox}}^{{\rm{dist}}}_{h\widetilde{\Phi}}(\tilde{\varrho}_{k-1}), \quad k\in\mathbb{N}, \quad \varrho_{0}(\bm{x}) := \rho_{0}(\bm{x})
\label{KineticProx}	
\end{align}

was established in \cite{duong2014conservative}.

>>>>

To set up a variational recursion of the form \eqref{InfiniteDimProxOpDef} for \eqref{TransformedPDEivp}, we set $(\Phi,{\rm{dist}}) \equiv \left(\widetilde{\Phi},\widetilde{W}\right)$ where
\begin{align}
\widetilde{\Phi}(\tilde{\rho}) := \int_{\mathbb{T}^{n} \times \mathbb{R}^{n}}\left(F(\boldsymbol{\eta})+\frac{1}{2} \log \tilde{\rho}\right) \tilde{\rho}\: \mathrm{d} \boldsymbol{\xi} \mathrm{d} \boldsymbol{\eta},
\label{Phitilde}	
\end{align}
and 
\begin{align}
\widetilde{W}^{2}\left(\tilde{\varrho}, \tilde{\varrho}_{k-1}\right):=&\inf _{\pi \in \Pi\left(\tilde{\varrho}, \tilde{\varrho}_{k-1}\right)}\!\int_{\mathbb{T}^{2 n} \times \mathbb{R}^{2 n}}\!\!\left\{\left\|\overline{\boldsymbol{\eta}}-\boldsymbol{\eta}+h \nabla_{\boldsymbol{\xi}} U(\boldsymbol{\xi})\right\|_{2}^{2}\right.\nonumber\\
&\hspace*{-0.2in}\left.+12\left\|\frac{\overline{\boldsymbol{\xi}}-\boldsymbol{\xi}}{h}-\frac{\overline{\boldsymbol{\eta}}+\boldsymbol{\eta}}{2}\right\|_{2}^{2}\right\} \mathrm{d} \pi(\boldsymbol{\xi}, \boldsymbol{\eta}, \overline{\boldsymbol{\xi}}, \overline{\boldsymbol{\eta}}).
\label{Wtilde}	
\end{align}
In \eqref{Wtilde}, $\Pi\left(\tilde{\varrho}, \tilde{\varrho}_{k-1}\right)$ denotes the collection of all joint PDFs supported on $\mathbb{T}^{2 n} \times \mathbb{R}^{2 n}$ that have finite second raw moments, with the first marginal $\tilde{\varrho}$, and the second marginal $\tilde{\varrho}_{k-1}$.

That the sequence of functions $\{\tilde{\varrho}_{k}\}$ for $k\in\mathbb{N}$, generated by the proximal recursion
\begin{align}
\tilde{\varrho}_{k} &= {\text{prox}}^{\widetilde{W}}_{h\widetilde{\Phi}}(\tilde{\varrho}_{k-1}) \nonumber\\
&\equiv \underset{\tilde{\rho}\in\mathcal{P}_{2}}{\arg\inf}\:\frac{1}{2}\widetilde{W}^{2}\left(\tilde{\varrho},\tilde{\varrho}_{k-1}\right) + h\:\widetilde{\Phi}(\tilde{\rho}), \quad \tilde{\varrho}_{0} := \tilde{\rho}_{0},
\label{KineticProx}	
\end{align}
converges to the flow generated by \eqref{TransformedPDEivp}, i.e., 
$$\tilde{\varrho}_{k}(\bm{\xi},\bm{\eta}) \xrightarrow{h\downarrow 0} \tilde{\varrho}(t=kh,\bm{\xi},\bm{\eta}),$$
was established in \cite{duong2014conservative}.

To compute \eqref{KineticProx}, we employ the probability-weighted scattered point cloud-based proximal algorithm proposed in \cite{caluya2019TAC}.
